### 2020-01-13 manuscript/bef_stability/manuscript.Rmd
Add total richness and research questions

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(7, 7),
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(magrittr)
library(cowplot)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
theme_set(theme_alain())
```

@@

@@

@@

```{r}
library(nlme)
library(piecewiseSEM)

st_basin <- get_basin_station()
myload(nmds, habitat_pressure, dir = mypath("report"))

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )

@@

## Diversity has a destabilizing effect on community

>>>>

knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(7, 7),
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(magrittr)
library(cowplot)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

theme_set(theme_alain())
```

@@

- Research questions:
  - What are the effects of the community structure on total biomass and stability ? 
    1. What are the effects of species richness on total biomass and stability ?
      - effect of species richness
      - effect of trophic group
    2. What are the effects of the community structure on total biomass and stability ?
      - What is the relative effect of the environment relative to the community
	structure ?
      - What is the effect of the community structure on the different
	parts of the stability + total biomass?
	- Effect of horizontal and vertical diversity

@@

```{r get-data}
library(nlme)
library(piecewiseSEM)

st_basin <- get_basin_station()
myload(nmds, habitat_pressure, dir = mypath("report"))
myload(op_analysis, dir = mypath("data"))

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )
```

### Relationship between stability and species richness

```{r}
stab_div_mod <- lme(data = sem_data,
  fixed = biomass_stab ~ richness_med,
  random = ~ 1 | basin/(alt + width)
)
rsquared(stab_div_mod, method = "nagelkerke")

```

@@

```{r}

@@

## Species richness has a destabilizing effect on community

### 2020-01-13 report/02-methods.Rmd
Add total richness and research questions

```{r pca-hab, fig.dim = c(7, 21), fig.cap = "PCA over habitat description"}
library(ade4)
library(factoextra)
pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_station), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)

@@

```{r}
dev.off()
m <- cor(as.matrix(select(na.omit(habitat_station), -station)), method = "spearman")
corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
```

@@

```{r split-rivers, fig.dim = c(7, 12)}
hab_type <- habitat_pressure %>%
  filter(station %in% op_analysis$station) %>%
  mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
  wide_bin = ifelse(width_river_mean > median(width_river_mean), TRUE, FALSE),
  hab_type = map2_chr(high_bin, wide_bin, function(high, wide){
    if (high) {
      if (wide) {
	"high_wide"
      } else {
	"high_narrow"
      }
    } else {
      if (wide) {
	"low_wide"
      } else {
	"low_narrow"
      }
    }

@@

hab_type_pca <- hab_type[hab_type$station %in% na.omit(habitat_station)$station, ]
match_st <- match(hab_type_pca$station, na.omit(habitat_station)$station)
hab_type_pca <- hab_type_pca[order(match_st), ]

@@

```{r}

@@

res_sync_occ_st %>%
  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
  ggplot(aes(x = richness_med, y = value)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type), rows = vars(stab))
```

>>>>

```{r pca-hab, fig.dim = c(7, 21), fig.cap = "PCA over habitat description"}
library(ade4)
library(factoextra)
pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_pressure), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)

@@

```{r}
dev.off()
m <- cor(as.matrix(select(na.omit(habitat_pressure), -station)), method = "spearman")
corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
```

@@

```{r split-rivers, fig.dim = c(7, 12)}
hab_type <- na.omit(habitat_pressure) %>%
  mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
  wide_bin = ifelse(width_river_mean > median(width_river_mean), TRUE, FALSE),
  hab_type = map2_chr(high_bin, wide_bin, function(high, wide){
    if (high) {
      if (wide) {
	"high_wide"
      } else {
	"high_narrow"
      }
    } else {
      if (wide) {
	"low_wide"
      } else {
	"low_narrow"
      }
    }

@@

hab_type_pca <- hab_type[hab_type$station %in% na.omit(habitat_pressure)$station, ]
match_st <- match(hab_type_pca$station, na.omit(habitat_pressure)$station)
hab_type_pca <- hab_type_pca[order(match_st), ]

@@

```{r, fig.dim = c(10, 7)}

@@

res_sync_occ_st %>%
  select(richness_tot, richness_med, biomass_stab, type) %>%
  gather(rich_type, richness, richness_med, richness_tot) %>%
  ggplot(aes(x = richness, y = biomass_stab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type), rows = vars(rich_type))
```

### 2020-01-13 report/05-stability.Rmd
Add total richness and research questions

```{r}
synchrony %>%
  left_join(hab_type, by = "station") %>%
  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
  ggplot(aes(x = richness_med, y = 1/cv_com)) +
  geom_point() +
  geom_smooth(method = "auto") +
  facet_grid(cols = vars(hab_type))
```

```{r}
synchrony %>%
  left_join(hab_type, by = "station") %>%
  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
  ggplot(aes(x = richness_med, y = 1/cv_com)) +
  geom_point() +
  geom_smooth(method = "auto")
```

>>>>

```{r}
synchrony %>%
  left_join(hab_type, by = "station") %>%
  ggplot(aes(x = richness_med, y = 1/cv_com)) +
  geom_point() +
  geom_smooth(method = "auto") +
  facet_grid(cols = vars(hab_type))
```

```{r}
synchrony %>%
  gather(rich_type, richness, richness_tot, richness_med) %>%
  ggplot(aes(x = log10(richness), y = log10(1/cv_com))) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(cols = vars(rich_type))
```
